Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-09-07 pnas/Towards.tex
updated ref and beginning of Sec 2

\begin{figure*}[h]
	\centering
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_1}
		\caption{$500$ micrographs \TODO{Tamir: I am redo the exp}}
	\end{subfigure} 
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_4}
		\caption{$2\times 10^3$ micrographs}
	\end{subfigure} 
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_40}
		\caption{$2\times 10^4$ micrographs}
	\end{subfigure} 
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_400}
		\caption{$2\times 10^5$ micrographs}
	\end{subfigure}
	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)). Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image. This does not require particle picking. A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly. Estimates are obtained from $500,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels), each containing $700$ image occurrences on average.}	
\end{figure*}

@@

\section{The detection limit} \label{sec:detectionlimit}

At high SNR, if $x$ is known, the support signal $s$ in~\eqref{eq:model} can be estimated via linear programming~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust}. 
However, in the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible, that is, one cannot reliably detect occurrences of $x$ in the micrograph $y$.

To support this claim, we consider a strictly simpler problem: suppose an oracle identifies for us one interval of length $L$ in the micrograph that either contains a full signal occurrence (plus noise), or contains just noise. Our task is to determine which one it is, that is, to determine whether the corresponding entry of $s$ is 0 or 1.
The oracle further provides the signal $x$, the probability $q$ that  the interval contains signal, and the noise variance $\sigma^2$.

>>>>

\begin{figure*}[h]
	\centering
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_1}
		\caption{$500$ micrographs \TODO{Tamir: I am redoing the exp}}
	\end{subfigure} 
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_4}
		\caption{$2\times 10^3$ micrographs}
	\end{subfigure} 
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_40}
		\caption{$2\times 10^4$ micrographs}
	\end{subfigure} 
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_400}
		\caption{$2\times 10^5$ micrographs}
	\end{subfigure}
	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)). Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image. This does not require particle picking. A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly. Estimates are obtained from $500,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels), each containing $700$ image occurrences on average.}	
\end{figure*}

@@

\section{The detection limit} \label{sec:detectionlimit}
% Can be added to an arxiv version
%At high SNR, if $x$ is known, the support signal $s$ in~\eqref{eq:model} can be estimated via linear programming~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust}. 
%However, in the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible, that is, one cannot reliably detect occurrences of $x$ in the micrograph $y$.
In the low SNR regime---even if $x$ is known---estimating the binary sparse signal $s$ is impossible, that is, one cannot reliably detect occurrences of $x$ in the micrograph $y$.
To support this claim, we consider a strictly simpler problem: suppose an oracle identifies for us one interval of length $L$ in the micrograph that either contains a full signal occurrence (plus noise), or contains just noise. Our task is to determine which one it is, that is, to determine whether the corresponding entry of $s$ is 0 or 1.
The oracle further provides the signal $x$, the probability $q$ that  the interval contains signal, and the noise variance $\sigma^2$.
